---
title: "Yogurt Project Team8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## SQL Code ################################################################################################
use retailer1;
show tables;

describe hshldDemograph;
describe itemsAttributes;
describe randItemSales;
describe storeItemSales;
describe survItemSales;

select * from hshldDemograph;
select * from itemsAttributes;
select * from randItemSales;
select * from storeItemSales;
select * from survItemSales;
## #########################################################################################################

## Load Data
```{r}
dir = "~/Desktop/GBA424 Analytics Design and Applications/Case2 Yogurt Flavors Case/Data"
setwd(dir)
library(ggplot2)
hshldDemograph <- read.csv("hshldDemograph.csv")
Demograph <- read.csv('hshldDemograph.csv')
Attributes <- read.csv('itemsAttributes.csv')
randItemSales <- read.csv('randItemSales.csv')
storeItemSales <- read.csv('storeItemSales.csv')
survItemSales <- read.csv('survItemSales.csv')
survQuestions <- read.csv('survQuestions.csv')
survResponses <- read.csv('survResponses.csv')
```

## Delete bad responses 
```{r}
### Get rid of all the bad responses from survey 
survResponses$V8 <- as.character(survResponses$V8)
survResponses$V9 <- as.character(survResponses$V9)
survResponses$difftime <- difftime(survResponses$V9, survResponses$V8, units = "mins")
mean(survResponses$difftime) 
### the average time customers took to finish the survey is about 28 mins, so we consider survery finished by >60 as bad responses
survResponses <- survResponses[survResponses$difftime <= 60, ]
### get rid of all the responses that are not finished
survResponses <- survResponses[survResponses$V10 == 1, ]
### get rid of all the responses finished before May.15, 2011
survResponses$Date <- as.Date(substring(survResponses$V8,1,10))
survResponses <- survResponses[-c(seq(1,11,by = 1)),]
### get rid of the response with incomplete Q12
test <- survResponses[,c(seq(15,37, by = 1))]
test <- test[-which(apply(test,1,function(x) all(is.na(x)))),]
test <- test[complete.cases(test),]
```

## 1) Describe the percentage of sales of existing flavors in the Greek yogurt category (all brands)
```{r}
############################################################################################################
## Outpt for Slide page3 ###################################################################################
############################################################################################################

df <- merge(Attributes,storeItemSales,by.x = "Item.Num", by.y = "Item.Num")
df1 <- df[df$Class=='GREEK',]
salesGreek <- aggregate(x=df1$Sales,by=list(df1$Flavor1),FUN = sum)
salesGreek$Percentage <- salesGreek$x/sum(salesGreek$x)
colnames(salesGreek)[1] <- 'Flavors'
colnames(salesGreek)[2] <- 'Sales'
write.csv(salesGreek,'salesGreek.csv') #export for visulization in Tableau

```

## 2) Describe the percentage of sales of existing yogurt flavors outside of Greek yogurt (regular class of yogurt)
```{r}
############################################################################################################
## Output for Slide page4 ##################################################################################
############################################################################################################

df2 <- df[df$Class!='GREEK',]
salesRegular <- aggregate(x=df2$Sales,by=list(df2$Flavor1),FUN = sum)
salesRegular$Percentage <- salesRegular$x/sum(salesRegular$x)
colnames(salesRegular)[1] <- 'Flavors'
colnames(salesRegular)[2] <- 'Sales'
write.csv(salesRegular,'salesRegular.csv') #export for visulization in Tableau
```

## 3) Describe survey respondents’ preferences for Greek yogurt flavors
```{r}
############################################################################################################
## Output for Slide page5 ##################################################################################
############################################################################################################

flavors <-c('almond','banana','blackcherry','blueberry', 'caramel', 'chai','chocolate','cinnamon',
            'coconut','honey', 'key-lime pie', 'lemon', 'mango', 'maple', 'peach','pineapple',
            'plain', 'pomegranate', 'raspberry', 'strawberry','strawberry-banana', 'vanilla',
            'vanilla-banana')
flavorpref0 <- t(as.data.frame(as.list(apply(test,2,function(x) sum(x==0)))))
flavorpref1 <- t(as.data.frame(as.list(apply(test,2,function(x) sum(x==1)))))
flavorpref2 <- t(as.data.frame(as.list(apply(test,2,function(x) sum(x==2)))))

flavorspref = as.data.frame(cbind(flavorpref0, flavorpref1, flavorpref2))
colnames(flavorspref) = c("0", "1","2")
row.names(flavorspref) = flavors

flavorspref$Percent0 = flavorspref$`0`/577
flavorspref$Percent1 = flavorspref$`1`/577
flavorspref$Percent2 = flavorspref$`2`/577
write.csv(flavorspref,'flavorspref.csv') #export for visulization in Tableau

```

## 4) Use TURF analysis to decide which flavor to launch next.(Not applicable aferter checking the result, so switched to another way.)
```{r}
############################################################################################################
## Result Mentioned is Slide page1, not applicable after checking ##########################################
############################################################################################################

df4 <- as.data.frame(test==0)
df4 <- as.data.frame(apply(df4,2,as.numeric))
colnames(df4)<-flavors

## TURF Analysis functions ##
measReach = function(data){
  if(is.null(dim(data))){ #if data is a vector
    ret = sum(data>0,na.rm=TRUE)/length(data)
  } else if(ncol(data)==1){ #if data has only one column
    ret = sum(data>0,na.rm=TRUE)/length(data)
  }
  else { #if data has multiple columns
    ret = sum(apply(data>0,1,any),na.rm=TRUE)/nrow(data)
  }
  return(ret)
}

evalNext = function(nextSet,set,data,measure=measReach){
  vals = numeric(length(nextSet)) #set up storage for return value
  for(k in 1:length(nextSet)){ #loop over the options in nextSet
    if(length(set)==0){         #if no existing options
      vals[k] = measure(data[,nextSet[k]]) 
    } else {                    #if existing options
      vals[k] = measure(data[,c(set,nextSet[k])])
    }
  }
  vals
}


evalFull = function(fullSet,data,origSet=numeric(0),measure=measReach){
  curSet = origSet; #the current set of included options
  remSet = fullSet[!(fullSet%in%origSet)]; #the remaining set of options to consider
  K = length(remSet)
  optVals = numeric(K); #create storage for the optimal values (optVals)
  ordSet = numeric(K); #create storage for ordered set
  for(i in 1:K){          #loop over the remaining set consider
    tmpVals = evalNext(remSet,curSet,data,measure); #calculate vector of next evaluations
    k = which.max(tmpVals) #pick the option that gives max measure, note will pick first case if a tie!
    optVals[i] = tmpVals[k] #add optimal value
    ordSet[i] = remSet[k]   #add index of option that creates optimal value
    curSet = c(curSet,ordSet[i]); #add optimal next option to current set
    remSet = remSet[-k];          #delete optimal next option from remaining set
  }
  #creaets a "TURF object" containing ordSet, optVals, origSet, origVal, measure, and pnames
  turf = list(ordSet=ordSet,optVals=optVals,origSet=origSet,origVal=measure(data[,origSet]),measure=measure,pnames=colnames(data))
  class(turf)="TURF" #makes the list into a TURF object so that can call plot.TURF
  turf  #return turf
}

#creates ggplot barplot for a turf object
plot.TURF=function(turf,...){
  if(class(turf)!="TURF"){
    cat("Object not a turf.")
  } else {
    df = with(turf,data.frame(vals = c(origVal,optVals),titles=paste(0:length(ordSet),c("Original",pnames[ordSet]),sep=":")))
    #with(turf,barplot(c(origVal,optVals),names.arg=c("Original",pnames[ordSet])))
    dodge = position_dodge(width=.75); ##to form constant dimensions positioning for all geom's
    gp = ggplot(df,aes(y=vals,x=titles))
    gp + geom_bar(position=dodge,stat="identity",col=1,fill=4,width=.75)
  }
}

## Running TURF analysis ##
turf1  = evalFull(c(1:23),df4,c(4,10,15,17,20,22))
plot(turf1)
turf2  = evalFull(c(4,10,15,17,20,22,3),df4,c(4,10,15,17,20,22))
plot(turf2)

############################################################################################################
## Result Mentioned is Slide page1, not applicable after checking ##########################################
############################################################################################################
```



